\section{July 21, 2014}

\subsection{Ownership Structures}
\begin{outline}
\1 Sole Proprietorship
\2 This is an ownership structure where one owner provides all the capital for the business. Usually the owner is also the manager, and makes all key business decisions. A sole proprietor will normally set up an A.B.N (Australian Business Number) and may make up a business name, however, in a legal sense a sole proprietorship is not a seperate legal entity from the owner.
\2 Advantages
\3 Total independence in decision-making
\3 Easy and inexpensive to set up as there are no registration fees and potentially less legal fees
\3 Taxed through individual income tax - progessive income tax rates apply
\3 All income goes to the owner
\4 The lowest block of income, $\$0$ to $\$18,200$, requires $0\%$ to go to the government.
\4 The second block of income, $\$18,200$ to $\$37,000$, requires $19\%$ to go to the government.
\4 The third block of income, $\$37,200$ to $\$80,000$, requires $32.5\%$ to go to the government.
\4 The fourth block of income, $\$80,000$ to $\$180,000$, requires $37\%$ to go to the government.
\4 The highest block of income, $\$180,000$ and above, requires $45\%$ to go to the government.
\2 Disadvantages
\3 Owners have unlimited liability, where they are obliged to use personal assets to pay off business debts
\3 Capital limited to owner's personal funds
\3 Limited expertise, and unable to share decision making
\3 More tax than private company once past 45\% with a progressive taxation system
\1 Partnership
\2 This is where 2-20 partners pool their resources to start a business. Usually a partnership agreement is drawn up that specifies the owner's stake in the business, responsibilities and share of the profits. Partnerships are not seperate entities from the owners, and therefore partnership shares are not transferable.
\2 Advantages
\3 Shared decision-making process
\3 Greater access to capital with more people
\3 As the tax free threshold can be claimed by each partner the total amount of tax paid is likely to be less.
\2 Disadvantages
\3 Profits shared among partners
\3 Having to compromise with partners
\3 Partners are jointly and severally liable, while still having unlimited liability
\3 Partnership dissolves if one partner leaves
\3 The tax rate is generally favourable, unless each partner earns over $\$180,000$ from their share of the profits.
\end{outline}
