\section{July 17, 2014}

\subsection{Small Business}
\begin{outline}
\1 Characteristics of small business
\2 The business has under 20 employees. A business with 1 to 5 employees is also classed as a micro-business.
\2 Ownership structures -- strictly for non-public businesses
\3 Sole proprietorship
\4 A sole proprietorship is where one person owns and manages a business. Variable tax rates apply proportionally to the income of the business and individuals.
\3 Partnership
\4 A partnership is a business where 2 to 20 people collectively own the business. Variable tax rates apply proportionally to the income of the business and individuals.
\3 Private company
\4 A private company is where a business is a separate legal entity to the owner. A private company can have 1 to 50 shareholders. A flat tax rate applies (30\%) to the business.
\2 Sources of finance
\3 Personal funds of the owner or owners can be used as a source of finance.
\3 Bank loans may be taken out as a source of finance.
\2 A small business is usually limited to one physical location. If the business is based around the internet, it is also possible to have zero physical locations.
\2 A small business usually has a relatively small market share.
\2 Small businesses often allow a high level of independence for the owner. 
\3 The exception is a franchise, where one buys the rights to a franchise in order to use their business model and use their name, which has pre-existing marketing and market share. This has the advantage of the business being already known, but the disadvantage of having little to no independence.
\1 Economic contributions of small business
\2 Small businesses contribute tax revenue to the government. The government can then re-invest this money into the economy.
\2 Small businesses represent 30 percent of the total workforce.
\2 Small businesses contribute a major amount of the Gross Domestic Product (GDP).
\2 Small business exports help reduce Australia's trade deficit.
\2 Small businesses stimulate activity in other sectors of the economy by either being a customer or a supplier to a larger business.
\end{outline}