\section{July 15, 2014}

\subsection{Business Stakeholders}
\begin{outline}
\1 Business stakeholders are anyone with a vested interest in the activities of a business.
\2 Internal Stakeholders main interest in a business
\3 Owners/Shareholders
\4 Owners and shareholders want the business to generate profits for the owners and shareholders. Shareholders can profit through dividends (share of profits) or capital gains (increased share price).
\3 Management
\4 Management want to achieve the business goals that set by the board or owners.
\3 Employees
\4 Employees want fair pay and good working conditions.
\2 External Stakeholders main interest in a business
\3 Customers
\4 Customers want good quality products or services, at a reasonable price.
\3 Suppliers
\4 Suppliers look to be paid on time and have advanced notice of orders. They also want continued business.
\3 Government
\4 Government are reliant on businesses for tax income. They are also responsible for making sure businesses meet legal requirements.
\3 Community
\4 The community wants the business to have a positive effect on society, to not sell harmful products, and to not damage the environment.
\1 Management of a business is complex, as managers must consider the interests of all the stakeholders when making decisions. 
\2 There are a number of situations withing managing a business where conflict of interests would arise.
\3 Examples
\4 Shareholders want dividends, but not possible without underpaying employees or raising the price for customers.
\4 Customers want good quality product, but business would be unable to pay suppliers for good quality product if they want keep the product at a 'reasonable price'.
\4 Management wants to achieve the businesses goals, but not possible without evading taxation.
\end{outline}

\subsection{Business Objectives}
\begin{outline}
\1 In the course of running a business, businesses must set goals, or objectives, to outline the direction the business wants to go, and what sort of impact it wants to make on the market.
\2 Examples
\3 Profitability
\3 Employee satisfaction
\3 Quality of product or service
\3 Customer service
\3 Customer satisfaction
\3 Market recognition
\3 Environmentally friendly
\3 Occupational Health \& safety
\end{outline}