\section{July 28, 2014}

\subsection{Business Plan Assessment Task}
\begin{outline}
\1 Business description
\2 A website-based service where people certified as translators can offer their services, and people who speak a language other than English can host an ad, or choose a translator to help with their everyday activities.
\1 Rationale for success
\2 The recent surge in immigration to Australia, particularly from Asian countries, has seen an increase in demand for translators, through people needing a translator in day-to-day activities, who either speak limited or no English. The potential, however, of an increase in demand for translators, has not been adequately met by any businesses offering real-time translation services. Starting a business in this market, which is primarily dominated by `freelancers', provides a means to fill the market need for translators in Australia, and establish itself as a recognised name internationally.
\1 Ownership structure and justification
\2 This business would be opened as a private company (Proprietary Limited), under regulations set by the Australian Securities \& Investment Commission. The reason for this is the potential the business has as large international service. Other ownership structures, such as sole proprietorship and partnerships, would be inadequate for this business, as they quickly become more expensive to run, particularly in taxation, as the profits increase. As a private company, the business would be controlled by a single director (with the potential to change), while being owned by its shareholders.
\end{outline}
